%%% A template to produce a nice-looking Curriculum Vitae.
%%% Kendall Giles <kendallgiles@gmail.com>
%%%
%%% Based on the original tempalte by Kieran Healy <kjhealy@gmail.com>
%%%
%%% ------------------------------------------------------------------------
%%% Requirements that are included in a modern tex distribution:
%%% ------------------------------------------------------------------------
%%% xelatex
%%% fontspec.sty
%%% hyperrref.sty
%%% xunicode.sty
%%% color.sty
%%% url.sty
%%% fancyhdr.sty
%%% memoir.cls
%%% fontawesome.sty
%%%
%%% 
%%% 
%%% ------------------------------------------------------------------------
%%% Requirements from https://github.com/kjhealy/latex-custom-kjh
%%% ------------------------------------------------------------------------
%%% org-preamble-xelatex.sty
%%% memoir-article-styles.sty
%%%
%%% ------------------------------------------------------------------------
%%% Optional
%%% ------------------------------------------------------------------------
%%% git
%%% vc.sty
%%% revnum.sty
%%% Fonts
%%%
%%% ------------------------------------------------------------------------
%%% Note
%%%------------------------------------------------------------------------
%%% Because this is a hand-tweaked file, be on the look out for \medksip, 
%%% \bigskip and \newpage commands here and there, which are used to balance
%%% the layout or avoid widows & orphans, etc. You should of course add or 
%%% remove these as needed.
%%%------------------------------------------------------------------------

\documentclass[11pt,article,oneside]{memoir}   
\usepackage{org-preamble-xelatex} 
\usepackage{fontspec}
\usepackage{fontawesome,url}

\usepackage{datetime}

\newdateformat{monthyeardate}{%
  \monthname[\THEMONTH] \THEYEAR}

%%%------------------------------------------------------------------------
%%% Metadata
%%%------------------------------------------------------------------------

%% Change as needed. Or just add me as a coauthor. Only some of these are 
%% used below in the hyperref declaration and address banner section.
\def\myauthor{Kendall Giles}
\def\mytitle{Vita}
\def\mycopyright{\myauthor}
\def\mykeywords{}
\def\mybibliostyle{plain}
\def\mybibliocommand{}
\def\mysubtitle{}
\def\myaffiliation{Virginia Tech}
\def\myaddress{Department of Electrical and Computer Engineering}
\def\myemail{giles@vt.edu}
\def\myweb{https://www.kendallgiles.com}
\def\myphone{}
\def\myfax{}
\def\mytwitter{@kendallgiles}
\def\myversion{}
\def\myrevision{}


\def\myaffiliation{Virginia Tech}
\def\myauthor{Kendall Giles}
\date{} % not used (revision control instead)
\def\mykeywords{Kendall, Giles, Kendall Giles, Vita, CV, Resume, Engineering}




%%%------------------------------------------------------------------------  
%%% Git version tracking 
%%%------------------------------------------------------------------------

%% If you don't use git or the vc package (from CTAN), comment this out.
%% If you comment it out, be sure to remove the \rfoot comment below, too.
%%\input{vc}


%%%------------------------------------------------------------------------
%%% Document
%%%------------------------------------------------------------------------
\begin{document}

%% Choose fonts for use with xelatex
%% Minion and Myriad are widely available, from Adobe. 
%% Pragmata is available to buy at http://www.fsd.it/fonts/pragma.htm
%% and is worth every penny. Any good monospace font will work fine, though.
%% Consolas or inconsolata are good alternatives.
\setromanfont[Mapping={tex-text}, 
	Numbers={OldStyle},
	Ligatures={Common}]{Hoefler Text}
\setsansfont[Mapping=tex-text,
	Ligatures={Common}, 
	Colour=AA0000]{Hoefler Text}
\setmonofont[Mapping=tex-text,Scale=0.72]{Hoefler Text} 

\newfontface\scheader[SmallCapsFont={Hoefler Text},SmallCapsFeatures={Letters=SmallCaps}]{Hoefler Text}

\newfontface\addressblock[Mapping={tex-text}, 
	Numbers={OldStyle},
	Ligatures={Common}]{Hoefler Text}


%%%------------------------------------------------------------------------
%%% Local commands
%%%------------------------------------------------------------------------

%% Marginal header
%% Note: as the document goes on you may need to introduce a (gradually increasing)
%% \vspace element to keep the marginal header pleasingly aligned with the first 
%% item in the body text. Like this: \marginhead{{\vskip 0.4em}Grants}, or 
%% \marginhead{{\vskip 0.8em}Service}. Experiment as needed.
\newcommand{\marginhead}[1]{\marginpar{\textsf{{\footnotesize\vspace{-1em}\flushright #1}}}}


%% [optional] custom ampersand (font consistent with the one chosen above)
% \newcommand{\amper}{{\fontspec[Scale=.95,Colour=AA0000]{Minion Pro Medium}\selectfont\&\,}}

%% No bullets on labels
\renewcommand{\labelitemi}{~} 

%% Custom hanging indent for vita items
\def\ind{\hangindent=1 true cm\hangafter=1 \noindent}
%\def\ind{\hangindent=18pt\hangafter=1 \noindent}
\def\labelitemi{~}
\renewcommand{\labelitemii}{~}

%%%------------------------------------------------------------------------
%%% Page layout
%%%------------------------------------------------------------------------

% These lines will insert git revision info in the footer, using the vc
% package---see docs for vc package for details. Comment out this line
% if you're not using vc, and also remove the \input{vc} line above.
\pagestyle{plain}
%%\thispagestyle{kjh}


%%%------------------------------------------------------------------------
%%% Address and contact block
%%%------------------------------------------------------------------------
\begin{minipage}[t]{0.595\textwidth}
 \flushright {\footnotesize 
 \href{https://ece.vt.edu}{Department of Electrical and Computer Engineering} \\ 302 Whittemore (0111) \\ Virginia Tech \\ \vspace{-0.05in} Blacksburg, \textsc{va} 24061}  
\end{minipage}
\begin{minipage}[t]{0.400\textwidth}
  \flushright \footnotesize  
  {\normalsize  \texttt{\href{\myweb}{\myweb}} \, \faGlobe} \\
  {\normalsize  \texttt{\href{https://twitter.com/kendallgiles}{\mytwitter}} \, \faTwitter }  \\ 
  {\normalsize  \texttt{\href{mailto:\myemail}{\myemail}} \, \faEnvelope} \\
\end{minipage}

\medskip
%% Name 
\noindent{\LARGE\scheader \textsc{kendall giles}} \\
\reversemarginpar
\noindent{\scheader \monthyeardate\today}

\bigskip       


%% Appointments
% \medskip
\marginhead{\sffamily appointments}

\ind Assistant Professor of Practice in Electrical and Computer Engineering, Virginia Tech, August 2016--Present.      

\ind Instructor in Electrical and Computer Engineering, Virginia Tech, May--August 2016. 

\ind Instructor for US Department of Veterans Affairs Accelerated Learning Program (through True Information Assurance LLC through Orions Arrow Inc), September 2015--May 2016.

\ind Research Scientist, Human Language Technology Center of Excellence (HLTCOE), Johns Hopkins University,  June--August 2015.

\ind Research Scientist, Human Language Technology Center of Excellence (HLTCOE), Johns Hopkins University,  June--August 2009.

\ind Assistant Professor in Statistical Sciences and Operations Research, Virginia Commonwealth University, January 2008--August 2011.

\ind Faculty Mentor and Research Fellow, Institute for Pure and Applied Mathematics, University of California--Los Angeles, Los Angeles, California, June--December 2007.


\ind Visiting Assistant Professor in Mathematics,
The College of William and Mary, January 2006--May 2007.

\ind Adjunct Instructor and Graduate Teaching Assistant in Information Systems, Virginia Commonwealth University, August 1998--December 2000, August--December 2001.

\bigskip

%% Education

\marginhead{\sffamily {{\vskip -0.23em} education}}

%\noindent\emph{Princeton University \vspace{0.01in}}

\ind PhD, Computer Science, Johns Hopkins University, May 2007.

\ind \hspace{0.35in} \footnotesize Dissertation: \emph{Knowledge Discovery in Computer Network Data: A Security Perspective}.\normalsize \vspace{0.05in}

\ind MFA, Creative Writing, University of Southern Maine, January 2013. 

\ind MS, Computer Science, Johns Hopkins University, May 2004. 

\ind MS, Information Systems, Virginia Commonwealth University, August 2002. 

\ind MS, Electrical Engineering, Purdue University, May 1993. 


\ind BS, Electrical Engineering, Virginia Tech, May 1991. 


\bigskip

%% Industry

\marginhead{\sffamily {{\vskip -0.23em} industry}}

\ind Senior Systems Engineer, Raytheon Systems, Falls Church, Virginia, May 2001--November 2005.

\ind Software Engineer, CUNA Mutual Credit Union and American Family Insurance (through SPR Technology Consultants), Milwaukee, Wisconsin, February 1996--August 1998.

\ind Software Engineer, GE Medical Systems, Milwaukee, Wisconsin, August 1991--February 1996.

\bigskip
 
%% Publications
\marginhead{\sffamily {\vskip 0.35em} publications}
\medskip
%%\noindent\emph{Book \vspace{0.01in}}

%%\ind  Kieran Healy. 2006. \emph{\href{http://www.lastbestgifts.com}{Last Best Gifts: Altruism and the Market for Human Blood and Organs}}. Chicago:~University of Chicago Press. \vspace{0.05in}

%%\ind \hspace{0.35in} \footnotesize Winner, Association for Research on Nonprofit Organizations and Voluntary Action (ARNOVA) Outstanding Book Prize. Finalist, C. Wright Mills Award. 

%%\vspace{-0.075in}

%%\normalsize

%%\bigskip
\noindent\emph{Journal Articles \vspace{0.05in}}
 
%% Use revnumerate environment if numbered publications are needed. 
%% (Include it above in the preamble).
%% \renewcommand{\labelenumi}{\textsc{a}\theenumi.}
%% \begin{revnumerate}

\ind Giles, K., M. Trosset, D. Marchette, and C. Priebe. “Iterative Denoising,” \emph{Computational Statistics}, 23:4, October, 2008.

\ind Fishkind, D., C. Priebe, K. Giles, L. Smith, and A. Aksakalli. “Disambiguation Protocols Based on Risk Simulation,” \emph{IEEE Transactions on Systems, Man, and Cybernetics, Part A}, 37:5, 814-823, September, 2007.

\ind Osei-Bryson, K. and K. Giles. “Splitting Methods for Decision Tree Induction: An Exploration of the Relative Performance of Two Entropy-Based Families,” \emph{Information Systems Frontiers Journal}, 8:195-209, Springer, July 2006.



\ind Osei-Bryson, K. and K. Giles. “An Exploration of a Set of Entropy-Based Hybrid Splitting Methods for Decision Tree Induction,” \emph{Journal of Database Management}, 15:3, 2004.


\ind Bryson, K., K. Giles, and B. Kositanurit. “Exploration of a Hybrid Feature Selection Algorithm,” \emph{Journal of the Operational Research Society}, 54:7, 790-797, 2003.


\ind Giles, K. “Understanding Ancient Martial Arts Texts: Pooh and Hermeneutics,” \emph{InYo: The Journal of Alternative Perspectives on the Martial Arts and Sciences}, December, 2000.




%% \ind Forthcoming. Kieran Healy and James Moody. ``Data Visualization in Sociology.'' \emph{Annual Review of Sociology.}


%\end{revnumerate}
%\newpage
\bigskip

\noindent\emph{Conference Proceedings \vspace{0.05in}}
 
%% Use revnumerate environment if numbered publications are needed. 
%% (Include it above in the preamble).
%% \renewcommand{\labelenumi}{\textsc{a}\theenumi.}
%% \begin{revnumerate}

\ind Giles, K., D. Marchette, and C. Priebe. “A Model of Backscatter as Escher Tessellations,” \emph{2005 Proceedings of the American Statistical Association, Statistical Graphics Section and Section on Statistics in Defense and National Security [CD-ROM]}, Alexandria, Virginia: American Statistical Association, 2005.

\ind Giles, K., D. Marchette, and C. Priebe. “On the Spectral Analysis of Backscatter Data,” \emph{Proceedings of the Hawaii International Conference on Statistics, Mathematics, and Related Fields}, 2004.

\ind Giles, K., D. Marchette, and C. Priebe. “The Development and Exploration of Online Classifiers for Backscatter from Denial of Service Attacks,” \emph{2004 Proceedings of the American Statistical Association, Statistical Computing Section [CD-ROM]}, Alexandria, Virginia: American Statistical Association, 2004.



\ind Giles, K., D. Marchette, and C. Priebe. “A Backscatter Characterization of Denial of Service Attacks,” \emph{2003 Proceedings of the American Statistical Association, Statistical Computing Section [CD-ROM]}, Alexandria, Virginia: American Statistical Association, 2003.


\ind Bryson, K. and K. Giles. “Splitting Methods for DT Induction: A Comparison of Two Families,” \emph{Proceedings of AMCIS 2002 (Americas Conference on Information Systems)}, Dallas, Texas, August 2002.

\ind Bryson, K., and K. Giles. “Attribute Discretization for Classification,” \emph{Proceedings of AMCIS 2001 (Americas Conference on Information Systems)}, Boston, Massachusetts, August 2001.

\ind Giles, K., K. Bryson, and Q. Weng. “Comparison of Two Families of Entropy-Based Classification Measures with and without Feature Selection,” \emph{HICSS (Hawaii International Conference on System Sciences)}, Wailea Maui, Hawaii, January 2001.

\ind Um, D., B. Stankovic, K. Giles, T. Hammond, and V. Lumelsky. “A Modularized Sensitive Skin for Motion Planning in Uncertain Environments,” \emph{Proceedings of the 1998 IEEE International Conference on Robotics and Automation}, Leuven, Belgium, May 1998.


%\end{revnumerate}
%\newpage

\bigskip

\noindent\emph{Technical Reports \vspace{0.05in}}

 
%% Use revnumerate environment if numbered publications are needed. 
%% (Include it above in the preamble).
%% \renewcommand{\labelenumi}{\textsc{a}\theenumi.}
%% \begin{revnumerate}

\ind Baker, K., Bethard, S., Bloodgood, M., Brown, R., Callison-Burch, C., Coppersmith, G., Dorr, B., Filardo, W., Giles, K., Irvine, A., Kayser, M., Levin, L., Martineau, J., Mayfield, J., Miller, S., Phillips, A., Philpot, A., Piatko, C., Schwartz, L., Zajic, D. “Semantically Informed Machine Translation,” \emph{Technical Report No. 002}, Human Language Technology Center of Excellence, Johns Hopkins University, Baltimore, Maryland, January 2010.

\ind Giles, K., D. Marchette, C. Priebe, and D. Waagen. “Iterative Denoising of Computer Network Application Traffic,” \emph{Technical Report No. 655}, Department of Applied Mathematics and Statistics, Johns Hopkins University, Baltimore, Maryland, November 2007.

\ind Giles, K., M. Trosset, D. Marchette, and C. Priebe. “Fast Iterative Denoising,” \emph{Technical Report No. 653}, Department of Applied Mathematics and Statistics, Johns Hopkins University, Baltimore, Maryland, December 2005.


%\end{revnumerate}
%\newpage

\bigskip

\noindent\emph{Other Publications \vspace{0.05in}}
% \renewcommand{\labelenumi}{\textsc{c}\theenumi.}
% \begin{revnumerate}

\ind “Expand Your Writing Potential with a Smart Notebook and Pen,” ProfHacker Column Guest Post, \emph{The Chronicle of Higher Education}, April 2018.

\ind “6 Life-Changing Ways Your Black Belt Journey Can Transform You,” Essay, \emph{Breaking Muscle}, October 2014.


\ind “Here to Help,” Flash Fiction, \emph{ThinkSmall7 Art Exhibition}, October-December 2013.

\ind “Rebel Yell,” Short Story, Included in the Anthology \emph{Surreal South ’13}, published by Press 53, October 2013.

\ind “What Color Is Your Dojo?,” Essay, \emph{Breaking Muscle}, July 2012.

\ind “Bartitsu: The Steampunk Mixed Martial Art,” Essay, \emph{Breaking Muscle}, October 2012. 

\ind \hspace{0.35in} \footnotesize Ranked \#4 in most popular martial arts articles at \emph{Breaking Muscle} for 2012.\normalsize \vspace{0.05in}


\ind “A Delicate Touch,” Short Story, \emph{Raw Dog Screaming Press}, October 2010. 

\ind \hspace{0.35in} \footnotesize Retrospective Writing Contest Winner.\normalsize \vspace{0.05in}

\ind “A Healing Place,” Short Story, \emph{The Dead Mule  School of Southern Literature Journal}, April 2010.
	
\ind “Parting Thoughts,” Essay, \emph{InYo: The Journal of Alternative Perspectives on the Martial Arts and Sciences}, January 2012.

\ind “Understanding Ancient Martial Arts Texts: Pooh and Hermeneutics,” Essay, \emph{InYo: The Journal of Alternative Perspectives on the Martial Arts and Sciences}, Reprint, July 2011.</li>
		
\ind “Understanding Ancient Martial Arts Texts: Pooh and Hermeneutics,” Essay, \emph{InYo: The Journal of Alternative Perspectives on the Martial Arts and Sciences}, December 2000.</li>
		

%\end{revnumerate}
%\newpage

%% \noindent\emph{Book chapters \vspace{0.05in}}
% \renewcommand{\labelenumi}{\textsc{c}\theenumi.}
% \begin{revnumerate}

%% \ind Kieran Healy. Forthcoming. ``Social Structure, Gifts and Norms in \emph{The Story of Qiu Ju},'' in \emph{Norms and Values: The Role of Social Norms as Instruments of Value Realisation}, edited by Michael Baurmann, Geoffrey Brennan, Robert E. Goodin and Nicholas Southwood. Baden Baden: Nomos Verlag.


%\end{revnumerate}

%% \bigskip 

%\newpage
%% \noindent\emph{Essays and reviews \vspace{0.05in}}

%\renewcommand{\labelenumi}{\textsc{r}\theenumi.}
%\begin{revnumerate}

%% \ind Kieran Healy. 2011. ``\href{http://www.kieranhealy.org/files/reviews/karpik-review.pdf}{Judgment and Distinction}.'' \emph{Socio--Economic Review} 9:~787--800. 


 
% %\end{revnumerate}
 \bigskip

%% Presentations
\marginhead{\sffamily {\vskip 0.5em}selected \newline talks \newline since 2007}
\medskip

\ind “Social Media for Academic Success,” STS 5424: Academic Publishing in Practice and Theory, Virginia Tech, Blacksburg, Virginia, April 2018.

\ind “Publishing: Inside a Literary Agency,” University of Southern Maine, Freeport, Maine, January 2013.

\ind “A Brief Look at Information Technology,” Copenhagen Business School, Copenhagen, Denmark, November 2012.

\ind “Doomsayers and Deniers: Data Analysis, Science, Politics, and Public Opinion in Climate Change,” Senior Symposium, Lynchburg College, Lynchburg, Virginia, February 2011.

\ind “What do You do with an Engineering Degree?” Student Engineers Council, College of Engineering, Virginia Tech, Blacksburg, Virginia, January, 2010.

\ind “An Introduction to R,” lecture for OPER/STAT 690 Research and Communications Seminar, and SYSM 681 Systems Seminar I, August 2009.

\ind “Consulting Experiences,” Panel Discussion, STAT/OR 490 Communications in Statistics and Operations Research, Virginia Commonwealth University, Richmond, Virginia, March 2009.

\ind “Knowledge Discovery with Iterative Denoising,” BINF739 Text Data Mining in Bioinformatics, Department of Bioinformatics and Computational Biology, George Mason University, Manassas, Virginia, March 2009.

\ind “Knowledge Discovery with Iterative Denoising,” Seminar, Computer Science Department, Virginia Commonwealth University, Richmond, Virginia, October 2008.

\ind “Interactive Text Analysis with Iterative Denoising,” Interface 2008, Text Data Analysis Session, Durham, North Carolina, May 2008.

\ind “Communication in Industry: Lessons Learned the Hard Way,” Lecture Presentation to STAT/OR 490: Communications in Statistics and Operations Research, Virginia Commonwealth University, Richmond, Virginia, April 2008.

\ind “Text Analysis with Iterative Denoising,” International Biometric Society, Eastern North American Region (ENAR), Arlington, Virginia, March 2008.

\ind “Iterative Denoising: A Flexible (and applicable to bioinformatics?) Knowledge Discovery Methodology,” Bioinformatics Colloquium, George Mason University, Manassas, Virginia, February 2008.

\ind “Scan Statistics on Enron Graphs,” Mathematics of Knowledge and Search Engines research program, University of California, Los Angeles, Institute for Pure and Applied Mathematics, Los Angeles, California, October 2007.

\ind “An Introduction to Google’s PageRank,” Mathematics of Knowledge and Search Engines research program, University of California, Los Angeles, Institute for Pure and Applied Mathematics, Los Angeles, California, September 2007.

\ind “Basics of Knowledge Discovery Engines,” Mathematics of Knowledge and Search Engines research program, University of California, Los Angeles, Institute for Pure and Applied Mathematics, Los Angeles, California, September 2007.


%% \ind ``Classification Situations.'' Yale University Center for Cultural Sociology, 2013.
 

%\end{revnumerate}

\bigskip
%\newpage

\marginhead{\sffamily {{\vskip -0.23em} teaching}}

\noindent\emph{Virginia Tech \vspace{0.05in}}

\ind ECE 5480: Cybersecurity and the Internet of Things, Graduate, 3 sections.

\ind ECE 5484: Fundamentals of Computer Systems, Graduate, 3 sections.

\ind CS 4264: Principles of Computer Security, Undergraduate, 1 section.

\bigskip

\noindent\emph{Virginia Commonwealth University \vspace{0.05in}}

\ind STAT 544: Statistical Methods II, Graduate, 1 section.

\ind STAT 736/OPER 736: Mathematics of Knowledge and Search Engines, Graduate, 2 sections.

\ind STAT 543: Statistical Methods I, Graduate, 1 section.

\ind STAT 541: Applied Statistics for Engineers and Scientists, Graduate, 5 sections.

\ind STAT 321: Introduction to Statistical Computing, Undergraduate, 2 sections.

\ind INFO 610: Analysis and Design of Database Systems, Graduate, 1 section.

\ind INFO 258: Visual Basic Programming, Undergraduate, 2 sections on campus and 1 section at WhiteOak Semiconductor, Richmond, Virginia.

\ind INFO 362: Computer Hardware and Software, Undergraduate, 1 section.

\ind INFO 291: Topics: Web Development, Undergraduate, 1 section at Software Development Center-Lee, the U.S. Army’s largest software development center, Fort Lee Army Base, Fort Lee, Virginia.

\ind INFO 491: Electronic Commerce, grading and lecturing, Undergraduate, 1 section. 



\bigskip

\noindent\emph{The College of William and Mary \vspace{0.05in}}

\ind M106: Elementary Probability and Statistics, Undergraduate, 4 sections.

\ind M351: Applied Statistics, Undergraduate, 2 sections.

\ind M410: Topics in Mathematics-Statistical Learning \& Applications to Text Analysis, Undergraduate, 1 section.

\ind M459: Guest Lecturer for Math 459: Knowledge Discovery for Bioinformatics, Undergraduate, January 2006.

\bigskip

\marginhead{\sffamily {\vskip -0.23em}grants \newline honors \newline \& awards}

\ind TechGirls Cybersecurity Summer Camp, Legacy International, U.S. State Department, \$16,500.00, 14-26 July 2019.

\ind Mentoring Program Project Grant, Virginia Tech Provost's Office, \$1,500.00, December 2016--May 2018.

\ind Summer Camp for Applied Language Exploration (SCALE) workshop, Johns Hopkins University, Baltimore, Maryland, June--August 2015.

\ind Short story “Here to Help” was displayed as a part of the international invitational ThinkSmall7 art exhibition in Richmond, Virginia, October--December 2013.

\ind Invited to read short story “Searching” at the international invitational ThinkSmall6 art exhibition at the Artspace gallery in Richmond, Virginia, 2011.

\ind Short story “A Delicate Touch” won the Raw Dog Screaming Press Retrospective Writing Contest, Judged by Michael Arnzen, October 2010.

\ind Summer Camp for Applied Language Exploration (SCALE) workshop, Johns Hopkins University, Baltimore, Maryland, June--August 2009.

\ind “A Hierarchical and Iterative System for the Analysis of Streamed Text Data,” Human Language Technology Center for Excellence, Baltimore, Maryland, \$7,512, Primary Investigator, May--September 2008.

\ind “The Design and Implementation of a System for Fusion and Inference from Multiple Disparate Data Sources,” Johns Hopkins University, \$102,560, Primary Investigator.  June 2009--May 2014.

\ind Virginia’s Center for Innovative Technology (CIT) Award, \$2,500, 1999.

\ind Graduate Teaching/Research Assistantship Award, Virginia Commonwealth University, Richmond, Virginia, 1998--1999, 1999--2000, 2000--2001.

\ind GE Night Out on the Town, GE Medical Systems, Milwaukee, Wisconsin, 1995.

\ind C.T. Tate University Distinguished Co-op Award, Virginia Tech, Blacksburg, Virginia, 1991.

\ind Litton Industries Scholarship, 1990--1991.

\ind Engineering Study Abroad Scholarship, (Switzerland, Germany), Virginia Tech, Blacksburg, Virginia, 1990.

\ind Association of Old Crows Scholarship, 1988--1989.

%\newpage

%% \marginhead{\sffamily {\vskip 1.12em}service to the \newline profession}
%% \medskip

%% \medskip


%% \marginhead{{\vskip 0.9em}Service to the \newline Profession}
%% \medskip

%%\medskip

\end{document}
